DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-09-20 paper/main.tex
intro revision

@@

In this paper, we present DeepPicar, or Picar for short, a low-cost
autonomous car platform that can be utilized in research and
education. We follow the same methodology found in other platforms,
such as NVIDIA’s end-to-end vision based control \cite{}, but
implement it on a smaller scale. The Picar is comprised of a Raspberry
Pi 3 Model B, a camera and a low cost RC car. By creating and using
the Picar platform, we seek to accomplish the following three
goals. First, the significant reduction of the overall cost required
would make autonomous driving research more accessible to interested
individuals/parties. Furthermore, it would remove the concerns of
creating replacement platforms as each part, or the entire system,
could be replaced relatively inexpensively. Second, the utilization of
a more cost-efficient platform would allow for a better understanding
of the performance requirements necessary for efficiently operating
autonomous vehicles. Finally, we strive to achieve the ability to
compare the real-time performance of multiple embedded computing
platforms.

@@

\section{Platform Overview}
...
\section{Data Collection}
...
\section{Network Architecture}
...
\section{Real-Time DNN Inferencing}
...
\section{Online/Offline Training}
...
\section{Evaluation}
...
\section{Related Work}
...
\section{Conclusion}
%-------------------------------------------------------------------------

>>>>

%% UPenn's f1/10 BOM: $3,628.37	
%% http://f1tenth.org/
%% http://selfdrivingcars.mit.edu/
%% http://fast.scripts.mit.edu/racecar/
%% https://github.com/mit-racecar

@@

In this paper, we present DeepPicar, a low-cost autonomous car
platform for research and education. From hardware perspective, 
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are very
affordable. The DeepPicar, however, employs state-of-the-art AI
techonologies, including a vision-based end-to-end control system that
utilizes a deep convolutional nueral network (CNN), which has 9
layers, about 27 million connections and 250 thousand parameters
(weights). The network architecture is in fact identifical to the one
used in Nvidia's DAVE-2 self-driving car~\cite{Bojarski2016}. Other
than the obvious difference in scale (RC car vs. real car), from the 
perspective of computing systems, the only differences between
our system and Nvidia's DAVE-2 are that our system is implemented in
TensorFlow~\cite{abadi2016tensorflow} and runs on a 
Raspberry Pi 3 whereas Nvidia's DAVE-2 systems is implemented in Torch
7~\cite{collobert2011torch7} and runs on a Drive PX self-driving car
computer~\cite{drivepx}, which is much more powerful but also a lot more
expensive.

%% We chose to use a Raspberry Pi 3 not only because of its
%% affordability and availability but also because it is representative
%% of today's mainstream low-end multicore processors, found in
%% smartphones, tables and other embedded devices.
%% The DeepPicar is comprised of a Raspberry
%% Pi 3 Model B, a camera and a low cost RC car.

By creating and using the Picar platform, we seek to accomplish the
following three goals. First, the significant reduction of the overall cost required
would make autonomous driving research more accessible to interested
individuals/parties. Furthermore, it would remove the concerns of
creating replacement platforms as each part, or the entire system,
could be replaced relatively inexpensively. Second, the utilization of
a more cost-efficient platform would allow for a better understanding
of the performance requirements necessary for efficiently operating
autonomous vehicles. Finally, we strive to achieve the ability to
compare the real-time performance of multiple embedded computing
platforms.

@@

\section{Platform Overview}
...
\section{Data Collection}
...
\section{Network Architecture}
...
\section{Real-Time DNN Inferencing}
...
\section{Online/Offline Training}
...
\section{Evaluation}
...
\section{Related Work}
\cite{Bojarski2016}

\section{Conclusion}
%-------------------------------------------------------------------------
